Environments and eval in R

### 2020-12-29 analysis/environments.Rmd
Renamed setup.R to functions.R

source("inc/latextags.R")
source("inc/setup.R")
source("inc/paths.R")
theme_set(theme_minimal())
create_tags(path(TAGS_DIR, "environments.tex"), prefix = "", default = TRUE)

>>>>

source("inc/latextags.R")
source("inc/functions.R")
source("inc/paths.R")
theme_set(theme_minimal())
create_tags(path(TAGS_DIR, "environments.tex"), prefix = "", default = TRUE)
